\documentclass[runningheads]{llncs}
\usepackage{aspPackage}

\newcommand{\papertitle}{Experimenting with robotic intra-logistics domains} 
\newcommand{\authorquote}{Gebser \etal}

\begin{document}

\title{A Summary of \papertitle}

\author{Jan Mensch}

\authorrunning{J. Mensch}

\institute{University of Potsdam\\ 
\email{jan.mensch@uni-potsdam.de}\\}


%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
This is a summary of the paper \textit{\papertitle}\cite{gebser2018experimenting}. In it \authorquote{}   present Asprilo, a framework for generating and visualizing benchmarks for Answer Set Programming (ASP) applications. A benchmark instance can be set in one of multiple domains. These domains all have a different focus and a varying degree of difficulty. 


\end{abstract}

\section{Introduction to Asprilo}

Asprilo is a benchmark framework for ASP applications\footnote{We assume that the reader is familiar with Answer Set Programming. If that is not the case, we recommend \cite{erdem2016applications}}. It was developed because other benchmarks are often not publicly available or do not provide enough examples. This, according to \authorquote{}, might slow down the development of ASP. 

The framework consists of a generator, a solution checker, a visualizer, and some reference encodings. A user is able to generate a problem instance using the generator. The problem instance can be part of any of the domains discussed in Section \ref{sec:problem}. The solution checker will review a given solution and the visualizer will represent this solution graphically. The visualizer will display the provides solution even if it is false. This way the visualizer can provide help when debugging an incorrect solution. The reference encoding provides examples on how to solve problem instances out of the domains discussed in Section \ref{sec:problem}.



\section{The Problem Domain} \label{sec:problem}

Asprilo aims to simulate the behavior of robots in a warehouse. In these problems robots have to fulfill orders. Each order can consist out of one or more objects which can be stored in a single or in multiple shelves. 

This problem was chosen because it can be designed in various levels of difficulty. This section introduces the four basic problem domains. An interested reader can find the full list of all domains in \cite{gebser2018experimenting}. The \textit{M} domain only concerns the movement of the robots. It resembles a multi-agent pathfinding scenario. In the \textit{C} domain, a single delivery action can fulfill multiple orders. The \textit{B} domain ignores the quantities of an order. In the \textit{A} domain quantities may not be ignored by the robot. The domains are subsets of each other (\textit{M} $\subseteq$ \textit{C} $\subseteq$ \textit{B} $\subseteq$ \textit{A})  and thus increase in difficulty. 



\section{Conclusion} \label{sec:conclusion}

The framework discussed provides the bases for a variety of possible benchmark instances. Among other things, it provides different problem domains with increasing difficulty and a visual debugger that can provide help, when trying to correct a false solution. It is the hope of \authorquote{}       that Asprilo will aid the development of the ASP paradigm. 



\begin{comment}
\section{Notes}

makespan: Total lenght of a schedule.

\begin{itemize}
    \item Introduction of asprilo 
    \item framework for benchmarking logical programmin. Complex scenarios like intra-logistics
    \item 1 intro strating here
    \item Why? Benchmarks are often classified or there are not enough examples. Missing benchmarks might slow down development of ASP
    \item Why use the problem of intra logistics? Warehouse layout is grid-based, easy abstraction for robot movement and you can discuss many problems with this example, e.g. charging actions or order frequencies. Because of this you can produce benchmarks with different complexity. 
    \item asprilo component: benchmark generator, solution checker, visualizer, reference encoding 
    \item 2 asprilos genarator 
    \item description of problem domain. Warehouse layout, definition of highways, shelfes, picking stations and storage locations. 
    \item Round based. Each robot can do one action per unit of time /round
    \item domain A: account for quantities in shelf
    \item domain B: simplifies A, by ignoring quantities of the products
    \item domain C: One delivery action can fulfill multiple orders
    \item domain M: resemble multi-agent path finding scenarios. Concerns only move actions. Shelfs remain on the spot. Robots have to find them.
    \item combination of domains. $A^M$, $B^M$, $C^M$ only singleton orders and one product per shelf. 
    \item instance generator: generate problem instance. Implemented in ASP, solved with multi-shot solving, controlled with Python API of clingo
    \item why multishot/incremental solving? First:  You can narrow down the search space. E.g. shelfs should only be placed on places where they are allowed to. Second: Threshold based domain-splitting. 
    \item a solution for a problem instance is a parallel plan, represented by a list of actions
    \item 3 visualization component 
    \item going through visualization capabilities. It can also do graphical editing. 
    \item 4 example encogings 
    \item Shows example encoding of scenario M
    \item 5 experimenting 
    \item All sorts of results from the experimenting stuff 
    \item 6 Related work
    \item other problems, that can be solved with logical programming
    \item Multi-agent path finding (MAPF) problem is quite important: collusion-free route fro each agent so that total time needed to fulfill task is minimal. Domain M corresponds to MAPF. TAPF as generalization of MAPF (grouping agents into teams) and G-TAPF is generalization of TAPF (number of tasks can be $>$ than number of agents). Asprillo is genereric and can thus be extended to include TAPF and G-TAPF
    \item 7 conclusion
    \item asprilo provides basic infrastructure for experimental studies of dynamic systems. 
    \item extendable in various ways (e.g. by introducing preferences to orders).
    \item experimental plattform for solving problems and benchmarking 
\end{itemize}
\end{comment}


\begin{comment}
\section{Questions}


\begin{itemize}
    \item Why do you use multi-shot solving for the instance generator? I do not understand the domain splitting. \textbf{Answer:} You want the instances to have some structure. So the instance should be similar to the instances that exist in reality. You need threshold based domain splitting to improve performance. You set variables in multiple steps. To reduce complexity. 
    \item \textbf{Notes:} Combinatorial problems. Place 55 shelves on 100 spots. Hard problem: Hard! First shelf on 100 spots, seconds on 99 spots... So 100 * 99 * 98 * ... * 45. So 100! - 45! which is just horrible :( 
    \item A solution is a list of actions. Will the generator create all possible solutions for a given problem instance? Is that not way too much work? \textbf{Answer:} No. The solver gets a generated solution and takes ASP rules. It will check solutions against the constraints.
    \item singleton order means one item per order? \textbf{Answer:} Yes. Oder consists of a pair of Item and Quantity. In a singleton the quantity is always 1.  
    \item Domains with lower case a. You will assign a task to the robots at first and then do the solving. This is domain splitting. Since you do domain splitting, the search space is reduced. Problem is that we might do a bad assignment. So we might not find the optimal solution. 
\end{itemize}
\end{comment}



\bibliographystyle{unsrt}
\bibliography{refs}

\end{document}
